Insert the article title here

### 2021-07-01 fstats_pca_lewontin.tex
small changes

\documentclass[12pt,a4pape, fullpage]{article}
\usepackage[
margin=1.5cm,
includefoot,
footskip=30pt,
]{geometry}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{url}

@@

First, we investigate the sparsity in the world overview data set: We find that the vast amount of contribution to the statistics comes from the first two PCs (Figure \ref{fig:f4}A). For example, the correlation between $F_4(X, Y, \text{Mozabite}, \text{Yoruba})$ and its approximation using the first two PCs is 99.2\%. To visualize the interpretation of $F_4$ as an angle, we use statistics of the form $F_4(X, \text{Sardinian}; \text{Mozabite}, \text{Yoruba})$, which can be interpreted as the angle between the vectors Mozabite-Yoruba and $X$-Sardinian. In Figure \ref{fig:f4}B, I show the angle based on two (blue), ten (green) and all PCs $red$. I find that for most Asian and American populations the angle is very close to 90°, as would be expected if the variation between African and non-African populations is mostly orthogonal. On the other hand, if $X$ is an African population, the angle is lower, and much less well approximated. This demonstrates that this PCA-plot likely does not model within-African population structure adequately.

>>>>

\documentclass[12pt,a4pape, fullpage]{article}
\usepackage[
margin=1.5cm,
includefoot,
footskip=30pt,
]{geometry}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{url}
\usepackage{textcomp}

@@

First, we investigate the sparsity in the world overview data set: We find that the vast amount of contribution to the statistics comes from the first two PCs (Figure \ref{fig:f4}A). For example, the correlation between $F_4(X, Y, \text{Mozabite}, \text{Yoruba})$ and its approximation using the first two PCs is 99.2\%. To visualize the interpretation of $F_4$ as an angle, we use statistics of the form $F_4(X, \text{Sardinian}; \text{Mozabite}, \text{Yoruba})$, which can be interpreted as the angle between the vectors Mozabite-Yoruba and $X$-Sardinian. In Figure \ref{fig:f4}B, I show the angle based on two (blue), ten (green) and all PCs $red$. I find that for most Asian and American populations the angle is very close to 90\textdegree, as would be expected if the variation between African and non-African populations is mostly orthogonal. On the other hand, if $X$ is an African population, the angle is lower, and much less well approximated. This demonstrates that this PCA-plot likely does not model within-African population structure adequately.
